JD notes on effects

### 2022-04-20 manuscript/jd_notes.Rmd
meeting prep

>>>>

We should talk about estimates before we get to confidence intervals.
The main thing about estimates is the reference point.
We should talk specifically about how taking the average as a reference point makes clear sense in a linear model.

We should talk about effect-style plots and prediction-style plots. A prediction-style plot is about predicting observations (or the ensemble mean of observations) for a given value of the focal predictor. For this, we want to use the classic curved confidence intervals (or prediction intervals). A prediction-style plot will generally focus on _total_ effects, and so will often be based on a univariate fit.

An effect-style plot is an attempt to visualize the effect of a focal predictor. In this case, we suggest the narrower confidence intervals. Here, it makes equal sense to think about the total effect of our focal predictor, from a univariate model, or the direct effects – after controlling for whatever – from a multivariate model.
